Discrete Quantum Theories and Computing

### 2019-03-29 dissertation.tex
dissertation.lyx "6.1 Conclusion" Updating...

Before what we can do further based on this thesis, let's summarize
what we have done previously.\todo{Keep writing\ldots}

>>>>

Before what we can do further based on this thesis, let's summarize
what we have done previously. In Chapter~\ref{chap:Conventional-Quantum-Theory},
we reviewed what was established in CQT. In particular, Sec.~\ref{CQC1qubitBloch.sec}
studied the geometrical structure of quantum states to prepare replacing
the conventional Hilbert space~$\mathComplex^{D}$ or projective
Hilbert space~$\CP{D-1}$ by its discrete analog in Chapter~\ref{chap:Unrestricted-Finite-Fields}
and~\ref{chap:DQT=000026DQC}. Since the replaced state spaces are
discrete, the quantum computation model could be built upon them naturally.
In Chapter~\ref{chap:Unrestricted-Finite-Fields}, the field of complex
numbers~$\mathComplex$ is replaced by unrestricted finite fields~$\Fq$,
and a valid pure state can be represented as any non-zero vector in
$\Fq^{D}$ and a measure scheme could be defined which only predicts
whether an measurement result is possible or not. \todo{Keep writing\ldots}
